---
title: "Coding Club Project"
output: html_notebook
---

# Overview

In this experiment, participated adapted to a 30 degree rotation with various types of feedback.

1. Regular cursor feedback (control)
2. Cursorjump feedback, where the rotation is shown at 1/3rd of the reach on each training trial (cursorjump)
3. A group where both the cursor and hand were visible during training (handview)
4. A group that was explained the rotation beforehand (instructed)

All reaches were to targets located at 45, 90, and 135 degrees.

Active localization conditions involved participants freely moving the robot arm within a specified angular range. 

Passive localization conditions involved participants hand being displaced by moving robot arm. 


# Data

There are several kinds of data we could analyze:

1. Training reaches
2. No-cursor reaches
3. Passive localization
4. Active localization

Active localization conditions involved participants freely moving the robot arm within a specified angular range. 

Passive localization conditions involved participants hand being displaced by moving robot arm. 

Participants data was collected for both aligned and rotated phases of the task.

# Analysis plan

- For reaches: calculate reach deviation at distance (1/4 of the reach)
- Hand localization: not yet



# Training -----

Did participants learn? Maybe we exclude some.

Did ALL groups learn to the same extent?

Did ALL groups learn quickly?

# No Cursors

There are two types of open-loop reaches. With or without strategy. We could subtract.

In groups with a difference between these two, there is definitely a strategy.

The difference between with and without strategy no-cursor reaches can be a measure of strategy.

# Hand localization

Is there a difference between active and passive localization?

Is there a difference in different conditions?

# Set up
```{r}
library('remotes')

ip <- installed.packages()

if ('Reach' %in% ip[,'Package']) {
    if (ip[which(ip[,'Package'] == 'Reach'), 'Version'] < "2023.12.17") {
      remotes::install_github('thartbm/Reach')
  }
} else {
  remotes::install_github('thartbm/Reach')
}

```

# Source project code
```{r}
# download and handle data:
source('R/data.R')

# scripts for training reaches:
source('R/reaches.R')
```

# Reach Training

1. Calculate Baseline (trials 31 - 45: 5 reaches per target)

2. Correct rotated reaches for baseline deviations
3. Plot learning curve
4. Fit exponential to the learning curve


